### 2020-08-03 manuscript.tex
benchmarking xml sessions

The simplest phylogenetic clock model -- the strick clock -- makes the convenient assumption that the evolutionary rate is constant across all lineages \cite{zuckerkandl1965evolutionary, kuhner1995estimating, larget1999markov}.  % Early examples? 
However, molecular substitution rates are known to vary over time, over population sizes, over evolutionary pressures, and over nucleic acid replicative machineries \cite{gillespie1994causes, woolfit2009effective, loh2010optimization}.
Moreover, any given dataset may be clock-like (where the substitution rate has a small variance across lineages) or non clock-like (a large variance). 
In the latter case, a strict clock is probably not suitable.

@@

8  &  80  &  1 &  10.0  &  4.2  &  \textit{Simulated data}  \\

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{/home/jdou557/Documents/Marsden2019/Months/July2020/fromVM/benchmarkingVM/ESS_round1.pdf}
\caption{\textbf{Rate parameterisation performance evaluation.} Comparison of ESS/hr (averaged across five independent MC3 analyses) with respect to relevant terms -- $P$: posterior density; $L$: likelihood, $p$: prior density, $r$: clock rate ESS averaged across all leaves, $\hat{r}$: branch rate mean, $v$: branch rate variance, $\sigma$: clock standard deviation, $\kappa$: HKY model transition-transversion ratio, $\lambda$: Yule model birth rate. $h$: tree height. Datasets are displayed in \textbf{Table \ref{table:datasets}}.  }
\label{fig:parameterisationResults}
\end{figure}

>>>>

The simplest phylogenetic clock model -- the strick clock -- makes the convenient assumption that the evolutionary rate is constant across all lineages \cite{zuckerkandl1965evolutionary, kuhner1995estimating, larget1999markov}.  % Early examples? 
However, molecular substitution rates are known to vary over time, over population sizes, over evolutionary pressures, and over nucleic acid replicative machineries \cite{gillespie1994causes, woolfit2009effective, loh2010optimization}.
Moreover, any given dataset may be clock-like (where the substitution rates have a small variance across lineages) or non clock-like (a large variance). 
In the latter case, a strict clock is probably not suitable.

@@

8  &  80  &  1 &  10.0  &  0.9  &  \textit{Simulated data}  \\

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1.pdf}
\caption{\textbf{Rate parameterisation performance evaluation.} Comparison of ESS/hr (averaged across five independent MC3 analyses) with respect to relevant terms -- $P$: posterior density; $L$: likelihood, $p$: prior density, $r$: clock rate ESS averaged across all leaves, $\hat{r}$: branch rate mean, $v$: branch rate variance, $\sigma$: clock standard deviation, $\kappa$: HKY model transition-transversion ratio, $\lambda$: Yule model birth rate. $h$: tree height. Datasets are displayed in \textbf{Table \ref{table:datasets}}.  }
\label{fig:parameterisationResults}
\end{figure}
